Matching bullets

### 2015-11-18 imaging-paper.Rnw
Ignore the pdf files
single datadir path

<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
opts_chunk$set(fig.path='Figure/fig-', cache.path='cache/', fig.align='center', fig.width=5, fig.height=5, fig.show='hold', par=TRUE, cache=F, tidy=T, concordance=TRUE, autodep=TRUE, root.dir="../", comment="|", dev="CairoPDF")
datadir <- "data"
imgdir <- "Figure/"
codedir <- "code"

@@

datadir <- "~/GitHub/x3prproto/images/Hamby252_3DX3P1of2/"

>>>>

<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
opts_chunk$set(fig.path='Figure/fig-', cache.path='cache/', fig.align='center', fig.width=5, fig.height=5, fig.show='hold', par=TRUE, cache=F, tidy=T, concordance=TRUE, autodep=TRUE, root.dir="../", comment="|", dev="CairoPDF")
imgdir <- "Figure/"
codedir <- "code"
datadir <- "app/images/Hamby252_3DX3P1of2/"

@@
